Data Descriptor: Corresponding author journal publishing activities 2014-2018

### 2019-10-28 analysis/paper.Rmd
grammar fix

As country-level consortia increasingly embrace transformative agreements as a means to increase the proportion of their research published open access [^1], the dataset constitutes a highly useful resource for researchers and practitioners alike. When combined with information on a country’s own subscription and hybrid APC expenditure, bibliometric data about corresponding author affiliation benefit cost modelling for a fully open access future national consortia can derive key insights such as

>>>>

As country-level consortia increasingly embrace transformative agreements as a means to increase the proportion of their research published open access [^1], the dataset constitutes a highly useful resource for researchers and practitioners alike. When combined with information on a country’s own subscription and hybrid APC expenditure, bibliometric data about corresponding author affiliation can help national consortia cost model for a fully open access future and derive key insights such as:
